CUNY SPS DATA 605 Final

### 2019-05-24 DATA605/MSilva_Final.Rmd
More work on the final

```{r, message=FALSE, warning=FALSE}
library(randomForest)
library(caret)
library(MASS)
library(Matrix)
library(matlib)
library(dplyr)
library(ggplot2)
library(tidyr)
library(kableExtra)
```

@@

```{r, echo=TRUE, eval=TRUE}
kaggle <- read.csv("Kaggle_House_Prices/train.csv") %>%
  # Removing outliers per http://jse.amstat.org/v19n3/decock.pdf
  filter(GrLivArea < 4000) %>% 
  # Filling in missing values with zeros where it makes sense
  mutate(BedroomAbvGr = replace_na(BedroomAbvGr, 0),
         BsmtFullBath = replace_na(BsmtFullBath, 0),
         BsmtHalfBath = replace_na(BsmtHalfBath, 0),
         BsmtUnfSF = replace_na(BsmtUnfSF, 0),
         EnclosedPorch = replace_na(EnclosedPorch, 0),
         Fireplaces = replace_na(Fireplaces, 0),
         GarageArea = replace_na(GarageArea, 0),
         GarageCars = replace_na(GarageCars, 0),
         HalfBath = replace_na(HalfBath, 0),
         KitchenAbvGr = replace_na(KitchenAbvGr, 0),
         LotFrontage = replace_na(LotFrontage, 0),
         OpenPorchSF = replace_na(OpenPorchSF, 0),
         PoolArea = replace_na(PoolArea, 0),
         ScreenPorch = replace_na(ScreenPorch, 0),
         TotRmsAbvGrd = replace_na(TotRmsAbvGrd, 0),
         WoodDeckSF = replace_na(WoodDeckSF, 0)) 
```

@@

```{r predict, comment=NA}
test <- read.csv("Kaggle_House_Prices/test.csv")
y_hat <- predict(fit, test)
submission <- data.frame(Id = test$Id, SalePrice = y_hat)
summary(submission)
```

*It appears there is an NA in the submission.  In the interest of getting my final turned in on time I will be using the median to plug that hole.*

```{r}
fill <- median(submission$SalePrice, na.rm = TRUE)
submission <- submission %>%
  mutate(SalePrice = replace_na(SalePrice, fill))
write.csv(submission, "submission.csv", quote = FALSE, row.names =  FALSE)
```

*My Kaggle score is* **0.47768** *and my username is* **mikesilva***.  I am ranked 4520 on the leaderboard.  I will try to improve this score when I have time.*

*This analysis is available on  [GitHub](https://github.com/mikeasilva/CUNY-SPS/blob/master/DATA605/MSilva_Final.Rmd).*

>>>>

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(randomForest)
library(caret)
library(MASS)
library(Matrix)
library(matlib)
library(dplyr)
library(ggplot2)
library(tidyr)
library(kableExtra)
```

@@

```{r, echo=TRUE, eval=TRUE}
kaggle <- read.csv("Kaggle_House_Prices/train.csv") %>%
  # Removing outliers per http://jse.amstat.org/v19n3/decock.pdf
  filter(GrLivArea < 4000)

fill_holes <- function(df){
  df %>%
    # Filling in missing values with zeros where it makes sense
    mutate(BedroomAbvGr = replace_na(BedroomAbvGr, 0),
           BsmtFullBath = replace_na(BsmtFullBath, 0),
           BsmtHalfBath = replace_na(BsmtHalfBath, 0),
           BsmtUnfSF = replace_na(BsmtUnfSF, 0),
          EnclosedPorch = replace_na(EnclosedPorch, 0),
          Fireplaces = replace_na(Fireplaces, 0),
          GarageArea = replace_na(GarageArea, 0),
          GarageCars = replace_na(GarageCars, 0),
          HalfBath = replace_na(HalfBath, 0),
          KitchenAbvGr = replace_na(KitchenAbvGr, 0),
          LotFrontage = replace_na(LotFrontage, 0),
          OpenPorchSF = replace_na(OpenPorchSF, 0),
          PoolArea = replace_na(PoolArea, 0),
          ScreenPorch = replace_na(ScreenPorch, 0),
          TotRmsAbvGrd = replace_na(TotRmsAbvGrd, 0),
          WoodDeckSF = replace_na(WoodDeckSF, 0)) 
}

kaggle <- fill_holes(kaggle)
```

@@

```{r predict, comment=NA}
test <- read.csv("Kaggle_House_Prices/test.csv") %>%
  fill_holes()
y_hat <- predict(fit, test)
submission <- data.frame(Id = test$Id, SalePrice = y_hat)
summary(submission)
```

*It appears that some of the predictions are incorrect since the minimum is negative.*

```{r}
write.csv(submission, "submission.csv", quote = FALSE, row.names =  FALSE)
```

*My Kaggle score is* **0.47769** *and my username is* **mikesilva***.  I am ranked 4520 on the leaderboard.  I will try to improve this score when I have time.*

*This analysis is available on  [https://github.com/mikeasilva/CUNY-SPS](https://github.com/mikeasilva/CUNY-SPS/blob/master/DATA605/MSilva_Final.Rmd).*
